\documentclass[conference]{IEEEtran}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Statistical Learning for Music Genre Recognition}

\author{
\IEEEauthorblockN{Santiago Florido Gomez}
\IEEEauthorblockA{
\textit{Dipl\^ome d'Ing\'enieur} \\
\textit{ENSTA Paris} \\
santiago.florido@ensta-paris.fr
}
\and
\IEEEauthorblockN{Gustavo Loiola Dos Santos}
\IEEEauthorblockA{
\textit{Dipl\^ome d'Ing\'enieur} \\
\textit{ENSTA Paris} \\
gustavo.loiola@ensta-paris.fr
}
}

\begin{document}

\maketitle

\begin{abstract}
\input{sections/abstract}
\end{abstract}

\input{sections/introduction}
\input{sections/data_preprocessing}
\input{sections/part1_unsupervised}
\input{sections/part2_binary}
\input{sections/part3_multinomial}
\input{sections/conclusion}

\begin{thebibliography}{1}
\bibitem{vandenberg2006preprocessing}
R.~A.~van den Berg, H.~C.~J.~Hoefsloot, J.~A.~Westerhuis, A.~K.~Smilde, and
M.~J.~van der Werf,
``Centering, scaling, and transformations: improving the biological information
content of metabolomics data,''
\emph{BMC Genomics}, vol.~7, art.~142, 2006,
doi:~10.1186/1471-2164-7-142.

\bibitem{feng2014log}
C.~Feng, H.~Wang, N.~Lu, T.~Chen, H.~He, Y.~Lu, and X.~M.~Tu,
``Log-transformation and its implications for data analysis,''
\emph{Shanghai Archives of Psychiatry}, vol.~26, no.~2, pp.~105--109, 2014,
doi:~10.3969/j.issn.1002-0829.2014.02.009.

\bibitem{nistskewness}
NIST/SEMATECH,
``Measures of Skewness and Kurtosis,''
\emph{NIST/SEMATECH e-Handbook of Statistical Methods},
Definition of Skewness, accessed Apr.~30, 2026.
Available: \url{https://www.itl.nist.gov/div898/handbook/eda/section3/eda35b.htm}

\bibitem{nistrankcorrelation}
NIST/SEMATECH,
``Rank Correlation Independence Test,''
\emph{Dataplot Reference Manual},
accessed May~1, 2026.
Available: \url{https://www.itl.nist.gov/div898/software/dataplot/refman1/auxillar/rankcorr.htm}

\bibitem{nistspreadlocation}
NIST/SEMATECH,
``Spread Location Plot,''
\emph{Dataplot Reference Manual},
accessed May~1, 2026.
Available: \url{https://www.itl.nist.gov/div898/software/dataplot/refman1/auxillar/slplot.htm}

\bibitem{psulogisticwald}
Penn State Department of Statistics,
``13.2 - Logistic Regression,''
\emph{STAT 501 Course Notes},
accessed May~3, 2026.
Available: \url{https://online.stat.psu.edu/stat501/lesson/13/13.2}

\bibitem{rsummaryglm}
R Core Team,
``summary.glm: Summarizing Generalized Linear Model Fits,''
\emph{R Manual, stats package},
accessed May~3, 2026.
Available: \url{https://stat.ethz.ch/R-manual/R-patched/RHOME/library/stats/html/summary.glm.html}

\bibitem{stepaicmass}
R Core Team,
``stepAIC: Choose a Model by AIC in a Stepwise Algorithm,''
\emph{R Manual, MASS package},
accessed May~3, 2026.
Available: \url{https://stat.ethz.ch/R-manual/R-devel/library/MASS/html/stepAIC.html}

\bibitem{raicdoc}
R Core Team,
``AIC: Akaike's An Information Criterion,''
\emph{R Manual, stats package},
accessed May~3, 2026.
Available: \url{https://stat.ethz.ch/R-manual/R-patched/RHOME/library/stats/html/AIC.html}

\bibitem{keribin2025supervised}
C.~Keribin,
``Apprentissage supervisé,'' 
\emph{APM\_4STA3\_TA -- M1 Mathématiques Appliquées, Université Paris-Saclay},
supports de cours, Partie II, 2025--2026.

\bibitem{rousseeuw1987}
P.~J.~Rousseeuw,
``Silhouettes: A graphical aid to the interpretation and validation of cluster analysis,''
\emph{Journal of Computational and Applied Mathematics}, vol.~20, pp.~53--65, 1987,
doi:~10.1016/0377-0427(87)90125-7.
\end{thebibliography}

\clearpage
\appendices
\input{sections/generative_tools}
\clearpage
\input{sections/supplementary_figures}

\end{document}
