\section{Introduction}
This project studies automatic musical genre recognition using a database composed of recordings from 60 performers. The material is organized into six categories, and for each performer, approximately 15 to 20 minutes of music were collected. These recordings were subsequently divided into 20 segments and parameterized.

The resulting descriptors combine standardized MPEG-7 audio features with cepstral coefficients and time-domain parameters. They summarize temporal, spectral, and envelope-related properties of each audio signal through statistical measures, such as mean values and variances computed either across frequency bands or over time.

The objective of this project is to study the information contained in the dataset through a descriptive analysis, followed by both univariate and multivariate analyses. Given the nature of the data, a filtering procedure is first implemented in order to select the most relevant and informative variables for the subsequent modeling stages.

After preprocessing, a principal component analysis (PCA) is proposed to explore the structure of the data in a reduced-dimensional space. In addition, an unsupervised classification approach based on hierarchical clustering with Ward's method is implemented, with the aim of comparing the obtained partitions with the true musical genre labels.

As a second component, supervised classifiers are constructed for the binary classification problem involving the \textit{Classical} and \textit{Jazz} genres. Several logistic regression models are considered: models including all available variables, models based on the most significant variables, and models obtained through stepwise variable selection. In order to compare their predictive performance, ROC curves are computed using the training data. The selection of a model of interest is then based on the area under the ROC curve (AUC), together with an analysis of the bias--variance trade-off associated with the implemented models.

Regularization strategies are also introduced through ridge logistic regression. In this case, the regularization parameter is estimated by means of 10-fold cross-validation on the training sample.

In the final part, the binary classification framework is extended to the nominal multinomial case in order to handle the five musical genres simultaneously. The multinomial logistic model is first formalized by choosing one genre as the reference category and expressing the class probabilities through a softmax-type link function. The likelihood, gradient, and Hessian are then derived to describe how the model parameters can be estimated numerically. A Newton-based implementation is critically analyzed, with particular attention to the numerical stability of the Hessian computation. Finally, the model is estimated using standard \texttt{R} functions, its performance is evaluated on both training and test data, and the multiclass results are interpreted through one-versus-rest ROC curves.